---
title: "frenchFISH_analysis_results"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

The images were aquired at 100x which results in 15.26 pixels/um. The tissue sections were 3um thick, therefore the thickness of the slice in pixels is 45.8 pixels. For sample PS09_287383C_Myc_Terc the average diameter of the nucleus appears to be 150 pixels.
```{r}
library(frenchFISH)
library(ggplot2)
library(xlsx)
library(reshape2)
library(cowplot)
library(tidyr)
library(gplots)
library(RColorBrewer)
library(gridExtra)
library(gridGraphics)
library(plyr)
library(dplyr)

path_to_dir <- "~" # change to be path to frenchFISH_analyses directory
setwd(paste(path_to_dir, "/frenchFISH_analyses/", sep = ""))

theme_set(theme_gray(base_size = 3))
my_theme<-theme_bw()+theme(axis.text=element_text(size=7),axis.title=element_text(size=7),
                           strip.text.x = element_text(size = 7),
                           strip.text.y = element_text(size = 7),
                           legend.text = element_text(size = 7),
                           panel.grid.minor = element_blank(),
                           panel.grid.major = element_blank(),
                           plot.title = element_text(size = 7, face = "bold",hjust=0.5))

#function to estimate the standard error
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,conf.interval=.95, .drop=TRUE)
{
  # New version of length which can handle NA's: if na.rm==T, don't count them
  length2 <- function (x, na.rm=FALSE) {
    if (na.rm) sum(!is.na(x))
    else       length(x)
  }
  
  # This does the summary. For each group's data frame, return a vector with
  # N, mean, and sd
  datac <- ddply(data, groupvars, .drop=.drop,
                 .fun = function(xx, col) {
                   c(N    = length2(xx[[col]], na.rm=na.rm),
                     mean = mean   (xx[[col]], na.rm=na.rm),
                     sd   = sd     (xx[[col]], na.rm=na.rm)
                   )
                 },
                 measurevar
  )
  
  # Calculate standard error of the mean
  datac$se <- datac$sd / sqrt(datac$N)  
  
  # Confidence interval multiplier for standard error
  # Calculate t-statistic for confidence interval: 
  # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
  ciMult <- qt(conf.interval/2 + .5, datac$N-1)
  datac$ci <- datac$se * ciMult
  
  return(datac)
}

getVsegFrac<-function(x,h,r)
{
  Vseg=pi*h*(r^2-x^2-h^2/12)
  Vsphere=4/3*pi*r^3
  Vseg/Vsphere
}

getAreaOverlappingCircles<-function(r,d)
{
  intersect<-2*(r^2)*acos(d/(2*r))-(d/2)*sqrt(4*(r^2)-d^2)
  area<-pi*(r^2)
  area-intersect
}

extractCountTable<-function(f,sheets)
{
  dat<-c()
  for(i in 1:sheets)
  {
    currsheet<-read.xlsx2(f,i,stringsAsFactors=F,colClasses="numeric")
    currsheet<-cbind(sheetID=i,currsheet)
    dat<-rbind(dat,currsheet)
  }
  dat
}

getCounts<-function(dat,r,h)
{
  #standard method
  adj<-2/mean(as.numeric(dat$aqua),na.rm=T)
  standard_aqua<-quantile(adj*mean(as.numeric(dat$aqua),na.rm=T),c(0.025,0.25,0.5,0.75,0.975),na.rm=T)
  standard_red<-quantile(adj*mean(as.numeric(dat$red),na.rm=T),c(0.025,0.25,0.5,0.75,0.975),na.rm=T)
  standard_green<-quantile(adj*mean(as.numeric(dat$green),na.rm=T),c(0.025,0.25,0.5,0.75,0.975),na.rm=T)
  
  #VAP
  mat_dat <- data.matrix(cbind(green=as.numeric(dat$green), red=as.numeric(dat$red), aqua=as.numeric(dat$aqua)))
  VAP_all <- getManualCountsEstimates(mat_dat, r, h, "max")
  VAP_aqua <- VAP_all[VAP_all$Probe=="aqua",][-c(1, 7)]
  VAP_red <- VAP_all[VAP_all$Probe=="red",][-c(1, 7)]
  VAP_green <- VAP_all[VAP_all$Probe=="green",][-c(1, 7)]
  names(VAP_aqua) <- c("2.5%", "25%", "50%", "75%", "97.5%")
  names(VAP_red) <- c("2.5%", "25%", "50%", "75%", "97.5%")
  names(VAP_green) <- c("2.5%", "25%", "50%", "75%", "97.5%")
  
  rbind(standard_aqua=standard_aqua, standard_red=standard_red, 
        standard_green=standard_green, VAP_aqua=VAP_aqua, 
        VAP_red=VAP_red, VAP_green=VAP_green)
}

getManualRadius<-function(filename,numSheets)
{
  dat<-extractCountTable(filename,numSheets)
  diams<-rowMeans(cbind(as.numeric(dat$diameter1),as.numeric(dat$diameter2)),na.rm=T)
  mean(diams[!is.na(diams)])/2
}

getManualCounts<-function(filename,numSheets,radius,h)
{
  dat<-extractCountTable(filename,numSheets)
  getCounts(dat,radius,h)
}

plotManualCounts<-function(dat)
{
  pdat<-melt(dat[,c(1,3,4,5)],id.vars=c(1))
  ggplot(pdat,aes(y=as.numeric(value),x=variable,fill=variable))+
    coord_flip()+geom_bar(stat ="identity")+
    facet_grid(sheetID ~ .)+
    scale_fill_manual(values=c("darkgreen","red","darkgoldenrod1"))+
    theme(strip.text.y = element_text(size = 8, angle = 0),axis.text.y = element_blank())+
    ylab("Number of spots")
}
```


Need to simulate data with different issues to test performance:
-nucleus subsampling
-varying control probe copy-number
-missing spot counts (varying percentages: +- 1,5,10,15)

```{r simluation}
r=9 #radius
h=3 #tissue section thickness
areas<-pi*(r^2)

samps<-50 #number of cells to simulate
control_probe<-2 #expected copy-number of the control/centromeric probe
long_out<-c()
#iteration_count<-0
use_presimulated_data<-FALSE

set.seed(1)

#if(!(use_presimulated_data)){
for(prob_overlap in c(0,0.1,0.3,0.5,0.8))
{
  for(noise in c(-0.20,-0.10,-0.05,0,0.05,0.10,0.20))
  {
    for(control_probe in 1:4) #vary the control probe number
    {
      for(rep in 1:20) #number of samples
      {
        for(i in 1:10) #true copy-number
        {
          priorx<-runif(samps,0,r-h/2) #choose the centre point of each nucleus in the section
          VavgFrac<-sapply(priorx,getVsegFrac,h,r) #get the fraction of the nucleus that is subsampled
          control<-c()
          probe<-c()
          for(j in VavgFrac)
          {
            control<-c(control,rpois(1,control_probe*j))
            probe<-c(probe,rpois(1,i*j))
          }
          if(noise<0) #working here, generate noise by adding or substracting points
          {
            inds<-sample(1:samps,round(abs(noise)*samps))
            control[inds]<-control[inds]-1
            control[control<0]<-0
            inds<-sample(1:samps,round(abs(noise)*samps))
            probe[inds]<-probe[inds]-1
            probe[probe<0]<-0
          }
          if(noise>0)
          {
            inds<-sample(1:samps,round(abs(noise)*samps))
            control[inds]<-control[inds]+1
            inds<-sample(1:samps,round(abs(noise)*samps))
            probe[inds]<-probe[inds]+1
          }
          if(prob_overlap>0)
          {
            k<-2
            areas<-pi*(r^2)
            olap<-rbinom(samps,1,prob_overlap)
            while(k<=length(probe))
            {
              if(olap[k]==1)
              {
                new_count<-probe[k]+probe[k-1]
                probe[k]<-new_count
                probe<-probe[-(k-1)]
                new_count<-control[k]+control[k-1]
                control[k]<-new_count
                control<-control[-(k-1)]
                areas[k-1]<-areas[k-1]+getAreaOverlappingCircles(r,runif(1,min=0.7,max=1)*r*2)
                olap<-olap[-(k-1)]
              }else{
                areas<-c(areas,pi*(r^2))
                k<-k+1
              }
            }
          }else{
            areas<-pi*(r^2)
            areas<-rep(areas, length(probe))
          }
          
          observed<-mean(probe)
          standard_diploid<-(observed/mean(control))*2
          
          # frenchFISH manual count correction
          probe_mat <- data.matrix(cbind(probe=as.numeric(probe)))
          probe_VAP <- getManualCountsEstimates(probe_mat, r, h)
          VAP_adj <- probe_VAP$mean
          
          # frenchFISH automatic count correction
          probe_acc <- data.matrix(cbind(area=as.numeric(areas), probe=as.numeric(probe)))
          probe_est <- getAutomaticCountsEstimates(probe_acc, r, h)
          pp_est <- probe_est$median
          
          long_out<-rbind(long_out,
                          c(rep,control_probe==2,i,observed,noise,"Observed",prob_overlap),
                          c(rep,control_probe==2,i,standard_diploid,noise,"ControlAdjusted",prob_overlap),
                          c(rep,control_probe==2,i,VAP_adj,noise,"frenchFISH_manual",prob_overlap),
                          c(rep,control_probe==2,i,pp_est,noise,"frenchFISH_auto",prob_overlap))
          #print("COUNT:")
          #print(iteration_count)
          #iteration_count <- iteration_count + 1
        }
      }
    }
  }
}
#}else{
#   long_out<-readRDS("simulated_data.rds")
#}
#saveRDS(long_out, file = "simulated_data.rds")

colnames(long_out)<-c("Replicate","DiploidControl","TrueCN","EstimatedCN","NoiseLevel","Method","ProbOverlap")
long_out<-data.frame(long_out,stringsAsFactors = F)
long_out[,1]<-as.numeric(long_out[,1])
long_out[,3]<-as.numeric(long_out[,3])
long_out[,4]<-as.numeric(long_out[,4])
long_out[,5]<-as.numeric(long_out[,5])
long_out[,7]<-as.numeric(long_out[,7])

long_out$Method<-factor(long_out$Method,levels = c("Observed","ControlAdjusted","frenchFISH_manual","frenchFISH_auto"))

line_width<-0.3
#no overlapping nuclei
pdat1<-long_out[long_out$ProbOverlap==0&!long_out$Method=="frenchFISH_auto",]
pdat1$Method<-plyr::revalue(pdat1$Method,c(frenchFISH_manual="FrenchFISH"))
error_p1<-ggplot(pdat1[pdat1$Method=="Observed",], aes(y=as.numeric(EstimatedCN),x=as.numeric(TrueCN),group=as.numeric(TrueCN))) + 
  geom_boxplot(lwd=line_width,outlier.size = line_width)+my_theme +
  facet_grid(NoiseLevel ~ Method)+geom_abline(lwd=0.3)+coord_cartesian(xlim=c(1,10),ylim=c(1,12))+
  scale_x_continuous(breaks=c(1:10),labels = c(rep("",4),5,rep("",4),10))+scale_y_continuous(breaks=c(1:10),labels = c(rep("",4),5,rep("",4),10))+
  theme(strip.text.y = element_blank(),axis.title.x=element_blank())+ylab("Estimated copy-number")+ggtitle("")
error_p2<-ggplot(pdat1[pdat1$DiploidControl==TRUE&!pdat1$Method=="Observed",], aes(y=as.numeric(EstimatedCN),x=as.numeric(TrueCN),group=as.numeric(TrueCN))) + 
  geom_boxplot(lwd=line_width,outlier.size = line_width)+my_theme +
  facet_grid(NoiseLevel ~ Method)+geom_abline(lwd=0.3)+coord_cartesian(xlim=c(1,10),ylim=c(1,12))+
  scale_x_continuous(breaks=c(1:10),labels = c(rep("",4),5,rep("",4),10))+scale_y_continuous(breaks=c(1:10),labels = c(rep("",4),5,rep("",4),10))+
  theme(strip.text.y = element_blank(),axis.title.x=element_blank(),axis.title.y = element_blank(),axis.text.y = element_blank())+ggtitle("Diploid control")
error_p3<-ggplot(pdat1[pdat1$DiploidControl==FALSE&!pdat1$Method=="Observed",], aes(y=as.numeric(EstimatedCN),x=as.numeric(TrueCN),group=as.numeric(TrueCN))) + 
  geom_boxplot(lwd=line_width,outlier.size = line_width)+my_theme +
  scale_x_continuous(breaks=c(1:10),labels = c(rep("",4),5,rep("",4),10))+scale_y_continuous(breaks=c(1:10),labels = c(rep("",4),5,rep("",4),10))+
  facet_grid(NoiseLevel ~ Method)+geom_abline(lwd=0.3)+coord_cartesian(xlim=c(1,10),ylim=c(1,12))+
  theme(axis.text.y = element_blank(),axis.title.x=element_blank(),axis.title.y = element_blank(),plot.margin = margin(5.5, 30, 5.5, 5.5, "pt"))+ggtitle("Non-diploid control")

#overlapping nuclei
pdat2<-long_out[!long_out$ProbOverlap==0&long_out$NoiseLevel==0&!long_out$Method=="frenchFISH_manual",]
pdat2$Method<-plyr::revalue(pdat2$Method,c(frenchFISH_auto="FrenchFISH"))

overlap_p1<-ggplot(pdat2[pdat2$Method=="Observed",], aes(y=as.numeric(EstimatedCN),x=as.numeric(TrueCN),group=as.numeric(TrueCN))) + 
  geom_boxplot(lwd=line_width,outlier.size = line_width)+my_theme +
  facet_grid(ProbOverlap ~ Method)+geom_abline(lwd=0.3)+coord_cartesian(xlim=c(1,10),ylim=c(1,12))+
  scale_x_continuous(breaks=c(1:10),labels = c(rep("",4),5,rep("",4),10))+scale_y_continuous(breaks=c(1:10),labels = c(rep("",4),5,rep("",4),10))+
  theme(strip.text.y = element_blank(),axis.title.x=element_blank(),panel.background = element_blank())+ylab("Estimated copy-number")+ggtitle("")
overlap_p2<-ggplot(pdat2[pdat2$DiploidControl==TRUE&!pdat2$Method=="Observed",], aes(y=as.numeric(EstimatedCN),x=as.numeric(TrueCN),group=as.numeric(TrueCN))) + 
  geom_boxplot(lwd=line_width,outlier.size = line_width)+my_theme +
  facet_grid(ProbOverlap ~ Method)+geom_abline(lwd=0.3)+coord_cartesian(xlim=c(1,10),ylim=c(1,12))+
  scale_x_continuous(breaks=c(1:10),labels = c(rep("",4),5,rep("",4),10))+scale_y_continuous(breaks=c(1:10),labels = c(rep("",4),5,rep("",4),10))+
  theme(strip.text.y = element_blank(),axis.title.x=element_blank(),axis.title.y = element_blank(),axis.text.y = element_blank(),panel.background = element_blank())+ggtitle("Diploid control")
overlap_p3<-ggplot(pdat2[pdat2$DiploidControl==FALSE&!pdat2$Method=="Observed",], aes(y=as.numeric(EstimatedCN),
                                                                                      x=as.numeric(TrueCN),group=as.numeric(TrueCN))) + 
  geom_boxplot(lwd=line_width,outlier.size = line_width)+my_theme +
  scale_x_continuous(breaks=c(1:10),labels = c(rep("",4),5,rep("",4),10))+scale_y_continuous(breaks=c(1:10),labels = c(rep("",4),5,rep("",4),10))+
  facet_grid(ProbOverlap ~ Method)+geom_abline(lwd=0.3)+coord_cartesian(xlim=c(1,10),ylim=c(1,12))+
  theme(axis.text.y = element_blank(),axis.title.x=element_blank(),axis.title.y = element_blank(),plot.margin = margin(5.5, 30, 5.5, 5.5, "pt"),panel.background = element_blank())+ggtitle("Non-diploid control")

source("heatmap3.R")

table_out<-long_out[,-1] %>%
  group_by(DiploidControl,TrueCN,NoiseLevel,Method,ProbOverlap) %>%
  summarise(accuracy=sum(abs(EstimatedCN-TrueCN)<0.5)/length(EstimatedCN),mean_abs_error=mean(abs(EstimatedCN-TrueCN)))

#table 1 with no overlap
table1<-table_out %>% filter(!Method=="frenchFISH_auto"&!Method=="Observed"&ProbOverlap==0) %>% as.data.frame(stringsAsFactors=FALSE)

table1_acc<-dcast(table1,DiploidControl+NoiseLevel + Method~TrueCN,value.var = "accuracy")
table1_acc<-table1_acc[order(table1_acc$DiploidControl,rev(table1_acc$Method),decreasing = T),]
table1_mae<-dcast(table1,DiploidControl+NoiseLevel + Method~TrueCN,value.var = "mean_abs_error")
table1_mae<-table1_mae[order(table1_mae$DiploidControl,rev(table1_mae$Method),decreasing = T),]
ColSideCol<-t(table1_acc[,c(1,2,3)])
cbPalette <- c(brewer.pal(8,"Dark2"),brewer.pal(9,"Set1"),"black")
ColSideCol<-as.matrix(plyr::revalue(ColSideCol,c("FALSE"="white","TRUE"="darkgrey",
                                                 "-0.20"=brewer.pal(3,"Blues")[3],
                                                 "-0.10"=brewer.pal(3,"Blues")[2],
                                                 "-0.05"=brewer.pal(3,"Blues")[1],
                                                 " 0.00"="white",
                                                 " 0.05"=brewer.pal(7,"Greens")[1],
                                                 " 0.10"=brewer.pal(7,"Greens")[2],
                                                 " 0.20"=brewer.pal(7,"Greens")[3],
                                                 "ControlAdjusted"=cbPalette[3],
                                                 "frenchFISH_manual"=cbPalette[6])))

par(xpd=TRUE,bg=NA)
heatmap.3(t(as.matrix(table1_acc[,c(-1,-2,-3)])),Rowv=NA,Colv=NA,scale="none",cellnote=t(round(table1_mae[,c(-1,-2,-3)])),
          dendrogram="none",trace = "none",col=c(rev(brewer.pal(8,"Reds"))[c(-1,-2,-3)],rep("white",2)),notecol="black",
          ColSideColors =t(ColSideCol),ColSideColorsSize=4,labCol="",ylab="True copy number",xlab="Mean absolute error")
legend("topright",inset=c(0.3,-0.1),legend=c("-20% noise",
                                             "-10% noise","-5% noise","Control Adjusted"),
       fill=c(brewer.pal(4,"Blues")[3],brewer.pal(4,"Blues")[2],brewer.pal(4,"Blues")[1],cbPalette[3]),
       border=FALSE, bty="n", y.intersp = 1.8, cex=0.7)
legend("topright",inset=c(0.05,-0.1),legend=c("5% noise","10% noise","20% noise","FrenchFISH"),
       fill=c(brewer.pal(4,"Greens")[1],brewer.pal(4,"Greens")[2],brewer.pal(4,"Greens")[3],cbPalette[6]),
       border=FALSE, bty="n", y.intersp = 1.8, cex=0.7)
error_heatmap<-recordPlot()


#table 2 with overlap
table2<-table_out %>% filter(!Method=="frenchFISH_manual"&!Method=="Observed"&NoiseLevel==0&ProbOverlap!=0) %>% as.data.frame(stringsAsFactors=FALSE)

table2_acc<-dcast(table2,DiploidControl+ProbOverlap + Method~TrueCN,value.var = "accuracy")
table2_acc<-table2_acc[order(table2_acc$DiploidControl,rev(table2_acc$Method),decreasing = T),]
table2_mae<-dcast(table2,DiploidControl+ProbOverlap + Method~TrueCN,value.var = "mean_abs_error")
table2_mae<-table2_mae[order(table2_mae$DiploidControl,rev(table2_mae$Method),decreasing = T),]
ColSideCol<-t(table2_acc[,c(1,2,3)])
cbPalette <- c(brewer.pal(8,"Dark2"),brewer.pal(9,"Set1"),"black")
ColSideCol<-as.matrix(plyr::revalue(ColSideCol,c("FALSE"="white","TRUE"="darkgrey",
                                                 "0.1"=brewer.pal(4,"Greens")[1],
                                                 "0.3"=brewer.pal(4,"Greens")[2],
                                                 "0.5"=brewer.pal(4,"Greens")[3],
                                                 "0.8"=brewer.pal(4,"Greens")[4],
                                                 "ControlAdjusted"=cbPalette[3],
                                                 "frenchFISH_auto"=cbPalette[6])))


par(xpd=TRUE,bg=NA)
heatmap.3(t(as.matrix(table2_acc[,c(-1,-2,-3)])),Rowv=NA,Colv=NA,scale="none",cellnote=t(round(table2_mae[,c(-1,-2,-3)])),
          dendrogram="none",trace = "none",col=c(rev(brewer.pal(8,"Reds"))[c(-1,-2,-3)],rep("white",2)),notecol="black",
          ColSideColors =t(ColSideCol),ColSideColorsSize=4,labCol="",ylab="True copy number",xlab="Mean absolute error")
legend("topright",inset=c(0.3,-0.18),legend=c("10% overlap",
                                              "20% overlap","50% overlap","80% overlap"),
       fill=c(brewer.pal(4,"Greens")[1],brewer.pal(4,"Greens")[2],brewer.pal(4,"Greens")[3],brewer.pal(4,"Greens")[4]),
       border=FALSE, bty="n", y.intersp = 1.8, cex=0.7)
legend("topright",inset=c(0,-0.18),legend=c("Control Adjusted","FrenchFISH"),
       fill=c(cbPalette[3],cbPalette[6]),
       border=FALSE, bty="n", y.intersp = 1.8, cex=0.7)
p4<-recordPlot()

top_row<-plot_grid(overlap_p1,overlap_p2,overlap_p3,nrow=1,labels=c("a","b","c"),rel_widths = c(1.1,2,2.5))+theme(panel.background = element_blank())
ggdraw(add_sub(top_row,"True copy-number",size=7))+theme(panel.background = element_blank())
grid.text("Probability of overlapping nuclei",rot=-90,x=0.96,gp=gpar(fontsize=7))
p5<-grid.grab()
p<-plot_grid(p5,p4,ncol=1,labels=c("","d"),rel_heights = c(0.55,0.45))

cairo_pdf("sim_overlap.pdf",height=7,width=5)
print(p)
dev.off()
```

Given the observed spotcounts per nucleus, we can infer lamda, the intensity of the underlying poisson distribution that generated the counts. So for the manual counts for sample PS09_287383C_Myc_Terc for tile 1 we have:
```{r}
#plot layout
#manual - standard
#manual - VAP
#automatic - standard
#automatic - VAP
#automatic - FrenchFISH

#manual counts
files<-c("rigorous_PS11_10021_2B_manual_spot_counting_2016_02_02.xls","rigorous_PS09_20676_2B_2015_01_18__Maunal_spot_counting_1.xls",
         "third_rigorous_PS09_28738_3C_2015_01_45__Maunal_spot_counting_3.xls","rigorous_PS11_16711_2015_01_18_Maunal_spot_counting_2.xls",
         "rigorous_BL_24216_manual_spot_counting.xls","rigorous_BL_24199_manual_spot_counting.xls",
         "rigorous_BL32007_manual_spot_counting_2016_02_07.xls","rigorous_BL32080_manual_spot_counting.xls",
         "SC_07.xls","SC_011.xls","SC_028.xls","SC_030.xls")

h=3*15.26

manualRadii<-c(mapply(getManualRadius,paste0("manual_counts/",files),c(5,2,3,5,4,5,5,1,5,2,2)))
names(manualRadii)<-c("JBLAB-221","JBLAB-178","JBLAB-165",
                      "JBLAB-236","JBLAB-2063","JBLAB-2047",
                      "JBLAB-2150","JBLAB-2151","SC_007",
                      "SC_011","SC_028","SC_030")

manualCounts<-mapply(getManualCounts,paste0("manual_counts/",files),c(5,2,3,5,4,5,5,1,5,5,5,5),manualRadii[1:12],h,SIMPLIFY=F)
names(manualCounts)<-c("JBLAB-221","JBLAB-178","JBLAB-165",
                       "JBLAB-236","JBLAB-2063","JBLAB-2047",
                       "JBLAB-2150","JBLAB-2151","SC_007",
                       "SC_011","SC_028","SC_030")

manualRadii[9]<-70
manualRadii[12]<-70

pdat<-cbind(plyr::ldply(manualCounts),Probe=c("aqua","red","green","aqua","red","green"),Method=c(rep("standard (manual)",3),rep("VAP (manual)",3)))
colnames(pdat)<-c("Patient",colnames(pdat)[-1])


#automatic counts
samples<-c("PS11_10021_2B_Myc_Terc","PS09_20676_2B_Myc_Terc","PS09_287383C_Myc_Terc",
           "PS11_167511L_Myc_Terc","BL_024216_Myc_Terc","BL024199_Myc_Terc",
           "BL32077_Myc_Terc","BL32080_Myc_Terc","SC_007",
           "SC_011","SC_028","SC_030" )
sampnames<-c("JBLAB-221","JBLAB-178","JBLAB-165",
             "JBLAB-236","JBLAB-2063","JBLAB-2047",
             "JBLAB-2150","JBLAB-2151","SC_007",
             "SC_011","SC_028","SC_030")

res<-c()
count<-1
for(sind in 1:12)
{
  samp<-samples[sind]
  files <- dir(paste("automatic_counts/",samp,sep=""), recursive=TRUE,
               full.names=TRUE, pattern="\\.csv$")
  summarydat<-c()
  ppred<-c()
  ppgreen<-c()
  ppyellow<-c()
  orig_red<-c()
  orig_green<-c()
  orig_yellow<-c()
  orig_area<-c()
  sred<-c()
  sgreen<-c()
  syellow<-c()
  area<-c()
  for(i in files)
  {
    dat<-read.csv(i,header=T,stringsAsFactors=F)
    dat<-dat[dat$area.of.nucleus>10000&!is.na(dat$area.of.nucleus),]
    sred<-c(sred,dat$num.of.R.probes)
    sgreen<-c(sgreen,dat$num.of.G.probes)
    syellow<-c(syellow,dat$num.of.Y.probes)
    area<-c(area,dat$area.of.nucleus)
    cdat<-c(sum(dat$num.of.G.probes),sum(dat$num.of.R.probes),sum(dat$num.of.Y.probes))
    if((nrow(dat)>0))
    {
      summarydat<-rbind(summarydat,
                        c(dat$filename[1],"green",sum(dat$num.of.G.probes)))
      summarydat<-rbind(summarydat,
                        c(dat$filename[1],"red",sum(dat$num.of.R.probes)))
      summarydat<-rbind(summarydat,
                        c(dat$filename[1],"yellow",sum(dat$num.of.Y.probes)))
      
      orig_green <- c(orig_green, dat$num.of.G.probes)
      orig_red <- c(orig_red, dat$num.of.R.probes)
      orig_yellow <- c(orig_yellow, dat$num.of.Y.probes)
      orig_area <- c(orig_area, dat$area.of.nucleus)
    }
  }
  colnames(summarydat)<-c("tile","spot","value")
  summarydat<-data.frame(summarydat,stringsAsFactors=F)
  summarydat$tile<-substr(summarydat$tile,6,12)
  
  r=manualRadii[sind]
  
  adj<-2/mean(syellow,na.rm=T)
  auto_standard_yellow<-quantile(adj*mean(syellow,na.rm=T),c(0.025,0.25,0.5,0.75,0.975),na.rm=T)
  auto_standard_red<-quantile(adj*mean(sred,na.rm=T),c(0.025,0.25,0.5,0.75,0.975),na.rm=T)
  auto_standard_green<-quantile(adj*mean(sgreen,na.rm=T),c(0.025,0.25,0.5,0.75,0.975),na.rm=T)
  
  #VAP
  mat_avp = data.matrix(cbind(yellow=as.numeric(syellow), red=as.numeric(sred), green=as.numeric(sgreen)))
  auto_VAP_all <- getManualCountsEstimates(mat_avp, r, h)
  auto_VAP_yellow <- auto_VAP_all[auto_VAP_all$Probe=="yellow",][-c(1, 7)]
  auto_VAP_red <- auto_VAP_all[auto_VAP_all$Probe=="red",][-c(1, 7)]
  auto_VAP_green <- auto_VAP_all[auto_VAP_all$Probe=="green",][-c(1, 7)]
  names(auto_VAP_yellow) <- c("2.5%", "25%", "50%", "75%", "97.5%")
  names(auto_VAP_red) <- c("2.5%", "25%", "50%", "75%", "97.5%")
  names(auto_VAP_green) <- c("2.5%", "25%", "50%", "75%", "97.5%")
  
  # Automatic count correction
  acc_mat <- data.matrix(cbind(area=as.numeric(orig_area), green=as.numeric(orig_green), 
                               red=as.numeric(orig_red), yellow=as.numeric(orig_yellow)))
  estAll <- getAutomaticCountsEstimates(acc_mat, r, h)
  estYellow <- estAll[estAll$Probe=="yellow",][-c(1)]
  estRed <- estAll[estAll$Probe=="red",][-c(1)]
  estGreen <- estAll[estAll$Probe=="green",][-c(1)]
  names(estYellow) <- c("2.5%", "25%", "75%")
  names(estRed) <- c("2.5%", "25%", "75%")
  names(estGreen) <- c("2.5%", "25%", "75%")
  
  res<-rbind(res,cbind(sampnames[sind],rbind(estYellow,estRed,estGreen,
                                             auto_standard_yellow[c(-3,-5)],auto_standard_red[c(-3,-5)],auto_standard_green[c(-3,-5)],
                                             auto_VAP_yellow[c(-3,-5)],auto_VAP_red[c(-3,-5)],auto_VAP_green[c(-3,-5)])))
  count<-count+1
}

res<-cbind(res,c("aqua","red","green"))
colnames(res)<-NULL
pdat<-pdat[,c(-3,-5)]
res<-cbind(res,Method=c(rep("FrenchFISH   (auto)  ",3),rep("standard   (auto)  ",3),rep("VAP   (auto)  ",3)))
colnames(res)<-colnames(pdat)
pdat<-rbind(pdat,res)

pdat$Method = factor(pdat$Method,levels(pdat$Method)[c(2,5,4,3,1)])

pdat$Patient = factor(pdat$Patient,rev(c("JBLAB-221","JBLAB-178","JBLAB-165",
                                         "JBLAB-236","JBLAB-2063","JBLAB-2047",
                                         "JBLAB-2150","JBLAB-2151","SC_007",
                                         "SC_011","SC_028","SC_030")))

shaded<-pdat[pdat$Method=="VAP (manual)",]
pdat<-pdat[pdat$Method%in%c("FrenchFISH   (auto)  ","VAP (manual)"),]#,"standard   (auto)  "),]


ggplot(pdat,aes(x=Method,y=as.numeric(get("50%")),colour=Method))+
  geom_point()+theme_bw()+coord_flip()+
  scale_y_continuous(breaks=1:10)+geom_hline(yintercept=1:10,lty=3)+
  facet_grid(Patient ~ Probe)+ylab("")+
  geom_errorbar(aes(ymin=as.numeric(get("2.5%")),ymax=as.numeric(get("97.5%"))))+theme(legend.position="none")


pdat2<-pdat %>% dplyr::select(Patient,"50%",Probe,Method)%>%spread(Method,"50%")
colnames(pdat2)<-c("Sample","Probe","Manual","FrenchFISH")
pdat2$Manual<-as.numeric(pdat2$Manual)
pdat2$FrenchFISH<-as.numeric(pdat2$FrenchFISH)
pdat2$Probe<-plyr::revalue(pdat2$Probe,c(aqua="SE7",green="cMYC",red="hTERT"))

ribbondata<- data.frame(x=c(-50, 0:10, 50),
                        ymin=c(  -50 - 1,
                                 0:10 - 1,
                                 50 - 1),
                        ymax=c(  -50 + 1,
                                 0:10 + 1,
                                 50 + 1)
)
ribbondata2<- data.frame(x=c(-50, 0:10, 50),
                         ymin=c(  -50 - 2,
                                  0:10 - 2,
                                  50 - 2),
                         ymax=c(  -50 + 2,
                                  0:10 + 2,
                                  50 + 2)
)

p<-ggplot(pdat2,aes(x=Manual,y=FrenchFISH,colour=Probe))+
  geom_ribbon(data=ribbondata2, aes(x=x,ymin=ymin,ymax=ymax, fill="< 2"),
              inherit.aes = FALSE, alpha = 0.4)+
  geom_ribbon(data=ribbondata, aes(x=x,ymin=ymin,ymax=ymax, fill="< 1"),
              inherit.aes = FALSE, alpha = 0.4)+scale_fill_manual(values=c("darkgrey","lightgrey"))+
  geom_point(size=2)+geom_abline(intercept=0,slope=1)+
  coord_cartesian(xlim=c(0,10),ylim=c(0,10))+labs(fill="Copy number\ndifference")+
  scale_shape_manual(values=1:12)+
  scale_y_continuous(breaks=0:10)+
  scale_x_continuous(breaks=0:10)

cairo_pdf("ovarian_results.pdf",height=4,width=5.5)
print(p)
dev.off()

#percentage in agreement
sum(abs(pdat2$Manual-pdat2$FrenchFISH)<1,na.rm=T)/35
```

